---
title: "Cherre coding challenge"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: journal
    
---

```{r setup, include=FALSE}
if (!require("flexdashboard")) install.packages("flexdashboard");library(flexdashboard)

```
Column {data-width=350}
-----------------------------------------------------------------------
### Setting up

Before running the code, you need to go to Session -- Set Working Directory -- To Source File Location.

First we will load libraries to deal with sqlite. Here we will use RSQLite (to establish the connection), DBI and dbplyr (to execute SQL query), dplyr (to connect tables within the database), DT (to display datatable in an interactive format) and flexdashboard (to build the dashboard page for the report).

Then we will connect to the SQLite database and save the database as testdb.
Let's take a closer look at the testdb we just connected to.

```{r}
#Load libraries
if (!require("RSQLite")) install.packages("RSQLite");library(RSQLite)
if (!require("DBI")) install.packages("DBI");library(DBI)
if (!require("dbplyr")) install.packages("dbplyr");library(dbplyr)
if (!require("dplyr")) install.packages("dplyr");library(dplyr)
if (!require("DT")) install.packages("DT");library(DT)

#set up database
testdb = dbConnect(SQLite(), dbname="testdb.db")
src_dbi(testdb)
```

Column {data-width=350}
-----------------------------------------------------------------------
### Data Description

We can see the testdb include multiple tables.In this case three of them are listed in the tbls row in the output above:

+ frequent_browsers
+ people
+ sites
+ sqlite_sequence
+ visits

Following are the tables in the database. From the instructions we know that our task is to find the ten people who have visited the most sites and list these people in descending order of the number of sites they've visited in a table called FrequentBrowsers. Therefore, the frequent_browsers table is empty. I have examined this table in SQLite and it has two columns: person_id and num_sites_visited.

Here are the columns included in each table:

+ people: id, first_name, last_name
+ sites: id, url
+ visits: personId, siteId, time_visited
+ sqlite_sequence: name, seq


Row {data-height=550 .tabset}
-----------------------------------------------------------------------

### Table. people


```{r}
datatable(as.data.frame(tbl(testdb,sql("SELECT * FROM people")))) 

```


### Table. sites

```{r}
datatable(as.data.frame(tbl(testdb,sql("SELECT * FROM sites"))))
```

### Table. visits

```{r}
datatable(as.data.frame(tbl(testdb,sql("SELECT * FROM visits"))))
```

### Table. sqlite_sequence

```{r}
datatable(as.data.frame(tbl(testdb,sql("SELECT * FROM sqlite_sequence"))))
```

Column {.tabset.data-width=200}
-----------------------------------------------------------------------

### Removing duplicates

From the sqlite_sequence table we know that there are 30 people and 100 sites. We also know the id for the person and id for the sites. First we need to check if there are duplicates in the dataset.


### Checking duplicates in sites table

```{r}
datatable(as.data.frame(tbl(testdb,sql("SELECT url, count(*) from sites group by id having count(*) > 1"))))
```

### Checking duplicates in people table

```{r}
datatable(as.data.frame(tbl(testdb,sql("SELECT first_name, last_name, count(*) from people group by first_name,last_name having count(*) > 1"))))
```

Column {}
-----------------------------------------------------------------------

### Making Adjustments

We can see the sites table does not contain duplicates, but the people table contains duplicates. Alena Jacobson has two personids. We need to find the id of this person and change his/her another personid to the same number.

```{r}
tbl(testdb,sql("SELECT id FROM people WHERE first_name = 'Alena' AND last_name = 'Jacobson'"))
```

Before changing this person's id, we need to join the people table and visits table. This will enable us to change that person's id more efficiently. After joining the table, we change Alena Jacobson's personid to 30.

```{r echo=TRUE}
new_df <- as.data.frame(tbl(testdb,sql("SELECT id, first_name,last_name, siteId FROM people JOIN visits ON people.id = visits.personId")))
#change the id of Alena Jacobson to 30
new_df <- new_df %>% mutate(id=replace(id,first_name=="Alena"&last_name=="Jacobson",30))
```

Then to find the ten people who have visited the most sites, we need to count the sites grouped by personId to get the number of times a person visit sites. Then we need to order them in descending order and get the first 10 people's records.

```{r echo=TRUE}
#calculate the 10 people who visited most sites
freq_browser <- new_df %>% group_by(id) %>% summarize(count=n_distinct(siteId))%>%arrange(desc(count))%>%slice(c(1:10))

colnames(freq_browser) <- c('person_id', 'num_sites_visited')
```

```{r eval=FALSE}
dbWriteTable(testdb,"frequent_browsers",freq_browser,append=TRUE)
```


After extracting the data, I saved them into the frequent_browsers table. 
And following is the table.


Column {}
-----------------------------------------------------------------------

### Table. frequent_browsers

```{r}
#Let's check the frequent_browsers table 
datatable(as.data.frame(tbl(testdb,sql("SELECT * FROM frequent_browsers"))))

```

### Ten people who have visited the most sites
```{r}
#Display the top 10 people names
datatable(as.data.frame(tbl(testdb,sql("SELECT first_name, last_name FROM people JOIN frequent_browsers ON people.id = frequent_browsers.person_id"))))

#Finally remember to disconnect from the database
dbDisconnect(testdb)
```

Column {}
-----------------------------------------------------------------------
### Disconnecting from the database

After exploring the database, we need to disconnect from the database. This is to prevent adding unnecessary modification to the database.

